---
<<<<<<< HEAD
title: "NYC Part2"
=======
title: "NYC Car Accident Analysis - Part2"
>>>>>>> c7267ce282a7f5e34d1bc9479a63a0ac4a9b038f
author: "Chengran Ouyang"
date: "`r format(Sys.Date())`"
output:
  html_document:
    theme: lumen
    number_sections: true
    font-family: Open Sans, sans-serif
    font-import: https://fonts.googleapis.com/css?family=Open+Sans
    code_folding: hide
    highlight: tango
editor_options: 
  chunk_output_type: console
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Preprocess


## Load Dataset and Packages


Let's continue our journey. First of all, I have to load the packages and the dataset, and preprocess the data.



```{r results='hide', message=FALSE, warning=FALSE}
# pacman package install required packages if not available 
if (!require("pacman")) install.packages("pacman") 
pacman::p_load(tidyverse, DT, lubridate, leaflet, leaflet.extras, maps, data.table, ggthemes, rebus, clue, shiny)
data <- fread("processed.csv", stringsAsFactors = F, data.table = FALSE, na.strings=c("NA","NaN","?", ""))
# data <- read.csv("green_tripdata_2016-02.csv", stringsAsFactors = F)
# data <- fread("green_tripdata_2016-02v2.csv", stringsAsFactors = F, data.table = FALSE, na.strings=c("NA","NaN","?", ""))

```


## Load model, Icon, and Color


Then, I loaded the data_kmeans model, new color palette, and Icon.


```{r results='hide', message=FALSE, warning=FALSE}
data1 <- data
set.seed(0)
# data_kmeans <- data_coord %>% kmeans(50,nstart=20)
# save(data_kmeans, file = "data_kmeans.rda")
load("input/data_kmeans.rda")

data1$cluster <- data_kmeans$cluster

pal <- colorNumeric(
  palette = "Blues",
  domain = data$cluster)

greentaxi <- makeIcon(
  iconUrl = "https://i.imgur.com/UVfnHVr.png",
  iconWidth = 38, iconHeight = 35,
  iconAnchorX = 19, iconAnchorY = 39
)

```


## Reproduce the Graph


I reproduce the last graph from study1.


```{r}
set.seed(0)
data1 %>% sample_n(size=10000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>%
  addCircleMarkers(~LONGITUDE, ~LATITUDE, radius = 1,
                   color = ~pal(cluster), fillOpacity = 0.001)
```


# Shiny App


## The final mission for the last objective

I set up the input options for longitude and latitude with sliders. Once that data is input, the program would make a prediction, for which cluster it belongs to, based on the input and kmeans model. Then, it would give 20 recommended accident spots within the cluster as well as the closest accident spot among the Top 20.

```{r echo=FALSE}
inputPanel(
  sliderInput("lng", label = "Longtitude:",
              min = -74.630, max = -73.179, value = -74, step = 0.001),
  
  sliderInput("lat", label = "Latitude:",
              min = 40.5, max = 41, value = 40.75, step = 0.001)
)

renderLeaflet({
  x <- data_frame(LONGITUDE= input$lng, LATITUDE= input$lat)
  (cluster_num <- cl_predict(data_kmeans,x))

  result <- data1 %>% filter(cluster==cluster_num)


  round_num <- 3
  top20 <- result %>% group_by(lng=round(LONGITUDE,round_num),lat=round(LATITUDE,round_num)) %>% 
  count() %>% arrange(desc(n)) %>% head(20)
  top20 %>% 
  leaflet() %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>%
  addCircleMarkers(~lng, ~lat, radius = 1,
                   color = "firebrick", fillOpacity = 0.001)%>%
  addMarkers(~lng, ~lat, label = ~as.character(paste("Number of Accidents:",top20$n)))

})

renderPrint({
  x <- data_frame(LONGITUDE= input$lng, LATITUDE= input$lat)
  (cluster_num <- cl_predict(data_kmeans,x))

  result <- data1 %>% filter(cluster==cluster_num)


  round_num <- 3
  top20 <- result %>% group_by(lng=round(LONGITUDE,round_num),lat=round(LATITUDE,round_num)) %>% 
  count() %>% arrange(desc(n)) %>% head(20)
  dist <- list()
  for (i in 1:20) {
    dist[i] <- abs(top20[i,1]-x[1])+abs(top20[i,2]-x[2])
  }

  num <- dist %>% which.min()

  paste("The closest accident spot is at the coordinate - Longitude:",top20[num,1]," Latitude: ",top20[num,2])
})

renderLeaflet({
  x <- data_frame(LONGITUDE= input$lng, LATITUDE= input$lat)
  (cluster_num <- cl_predict(data_kmeans,x))

  result <- data1 %>% filter(cluster==cluster_num)


  round_num <- 3
  top20 <- result %>% group_by(lng=round(LONGITUDE,round_num),lat=round(LATITUDE,round_num)) %>%
  count() %>% arrange(desc(n)) %>% head(20)
  dist <- list()
  for (i in 1:20) {
    dist[i] <- abs(top20[i,1]-x[1])+abs(top20[i,2]-x[2])
  }

  num <- dist %>% which.min()

  top20[num,] %>%
  leaflet() %>%
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>%
  addCircleMarkers(~lng, ~lat, radius = 1,
                   color = "firebrick", fillOpacity = 0.001)%>%
  addMarkers(~lng, ~lat, label = ~as.character(paste("Number of Accidents:",top20$n)))


})
```





